Conflict Analysis for Mixed-integer SDPs

### 2022-06-15 tex/ConflictAnalysis.tex
add first overview of literature

>>>>

The original intention of conflict analysis was to derive useful
information from infeasible subproblems in a branch-and-bound
procedure. There are two types of conflict analysis: 
\begin{itemize}
\item If infeasibility was determined using propagation of variable bounds,
  one can use a graph-based conflict analysis. Here, a directed graph
  encodes the dependency of bound changes on each other, i.e., whether one
  bound was used to strengthen the other bound. One can then try to find a
  small subset of bound changes that arise from branching decisions that
  still lead to infeasibility. One can then add constraints that enforce
  that at least one branching decision is taken in a different
  way. See~\cite{Ach07b,Ach07} for more information in the context of MIPs.

  This kind of conflict analysis can also be used in the context of MISDPs
  and has already been investigated in~\cite{MatP22}. Overall, this kind of
  conflict analysis was not beneficial.
\item If the relaxation is infeasible, there are two ways to derive
  conflict information: The first is a greedy approach, which relaxes some
  of the branching decisions leading to the current relaxation as long as
  the relaxation remains infeasible. Then a constraint as in graph-based
  conflict analysis can be derived. See~\cite{Ach07b,Ach07} for more
  information in the context of MIPs.

  The other method is to use dual information to derive valid inequalities,
  which can then be propagated during the tree. This is called dual ray
  analysis by Witzig~\cite{Wit22} (see also \cite{WitBH17}). We follow this
  approach in the following.
\end{itemize}
